Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
small
typo

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with multi-staged verification phase}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{CEGIS with multi-staged verification phase.}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
Then, it is sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.

@@

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not be violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$. 
\todo{discuss the computation of the completeness threshold}

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with multi-staged verification}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{CEGIS with multi-staged verification.}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not violated for any $k>\overline{k}$. 
Then, it is sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.

@@

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$. 
\todo{discuss the computation of the completeness threshold}
